Misc Code

### 2019-03-28 Misc Code.Rmd
do not extract course description anymore since we do not use it in any analysis

>>>>

# Extracting description (UCM only)

Since the overviews contain a lot of information that does not interest us, we extract the description section from the overviews. The description section contains a brief description (200-500 words) of the content of the course. To accomplish this, for each overview, we need to identify the line where the description starts and the line where it ends. The description section is always preceeded by a header saying *Description* or *Course Description* (`start_descrip`), making it relatively easy to find the starting line of the decription section with `grep`. The description section is usually followed by the literature section which starts with header saying *Literature*, *Recommended Literature* or similar (see `end_descrip`). Using `grep` together with `end_descrip`, we can again identify the ending line of the description section of almost all overviews. A handful overviews do not contain a *Literature* section. For these, the section *Instructional Format* marks the end of the description section.

```{r description set up}
start_descrip  <- c("^Description", "^Course Description") %>% collapse_or
end_descrip    <- c(
  "^Recommended Literature", "^ ?Required Litera", "^ ?Literature$", "Literature \\(all",
  "^Instructional format$"
  ) %>% collapse_or
```

```{r description helper function}
is_start_descrip   <- function(string) string %>% str_detect(pattern = start_descrip )
is_end_descrip     <- function(string) string %>% str_detect(pattern = end_descrip   )
```

```{r extract_description}
extract_description <- function(overview){

  overview %>%

    split %>% tibble(line = .) %>%

    mutate(
      is_start_descrip = line %>% is_start_descrip,
      is_end_descrip   = line %>% is_end_descrip # Having multiple ends (e.g. "literature" and "instructional format") is ok because we only use the first (cumany)
      ) %>%

    # filter the description section
    mutate(
      is_after_start_descrip = cumany( is_start_descrip),
      is_before_end_descrip  = cumall(!is_end_descrip  ),
      is_descrip             = is_after_start_descrip & is_before_end_descrip
      ) %>%

    filter(is_descrip, !is_start_descrip, !is_end_descrip) %>%

    summarise(description = str_c(line, collapse = " ")) %>%

    pull

}
```

```{r description}
d_text$description <- d_text$overview %>% mutate(text = text %>% map_chr(extract_description))
```
